Data Management for LSST Special Programs

### 2023-05-20 DMTN-065.tex
Update DMTN-065.tex

Recommendations for the specific implementations needed to fulfill these requirements and maximize science from
Special Programs are provided on a case-by-case basis, with examples.

Hardware and processing boundaries on the potential diversity of data from Special Programs 
(e.g., longer or shorter exposure times), and the ability of the Data Management System to
process this data, and also provided along with a discussion of when user-generated processing 
and data products will be needed to meet some science goals.

The main target audience of this document is Rubin Observatory staff -- the construction- and operations-era Data Management
teams -- but members of the science community who are planning to use Special Programs to reach their science goals may also 
find this document useful.
}

@@

\input{sec_intro.tex}
x
\input{sec_sci.tex}

>>>>

\smallskip
Recommendations for the specific implementations needed to fulfill these requirements and maximize science from
Special Programs are provided on a case-by-case basis, with examples.

\smallskip
Hardware and processing boundaries on the potential diversity of data from Special Programs 
(e.g., longer or shorter exposure times), and the ability of the Data Management System to
process this data, are also provided along with a discussion of when user-generated processing 
and data products will be needed to meet some science goals.

\medskip
The main target audience of this document is Rubin Observatory staff -- the construction- and operations-era Data Management
teams -- but members of the science community who are planning to use Special Programs to reach their science goals may also 
find this document useful.
}

@@

\input{sec_intro.tex}

\input{sec_sci.tex}
